Tests of measurement invariance via stochastic processes: {S}ome properties

### 2013-07-25 frontiers/frontiers.Rnw
Rolled frontiers.Rnw back to r222
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/semtools@224 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

where $x_{i}$ is the data vector for individual $i$, $t_{i}$ is the latent variable for variable $i$ that the scales purport to measure, and $f$ is the model's distributional form \citep{}. If the cut point of $v$ is known in advance, i.e. gender, nested multiple group models\citep{} coupled with likelihood ratio test are most commonly applied. 
Suppose there are two groups A and B. The null hypothesis of measurement invariance is

@@

To be more specific, in the following section, we will introduce how to implement multi group analysis in lavaan package. For more details, see\citep{}
\subsection{Multiple Group Analysis}
First of all, we need to read in data to R.  
<<read data>>=
# Reading in the data
## (need data here)Data <- read.table("example.dat")
## names(Data) <- c("y1","y2","y3","y4","y5","y6","g")
@
Second, the model need to be specified using lavaan package. 
<<specify model>>=
library(lavaan)
model <- 'f1=~NA*y1+y2+y3
          f2=~NA*y4+y5+y6
          f1 ~~1*f1
          f2 ~~1*f2'
@
Third, we want to test which parameter(s) violate measurement invariance. In lavaan package, loading, manifest variables' intercept and factor means could be tested together or specifically. For more details, please see \citep{}. Since in most cases researchers are interested in the factor loading invariance, we will use that as the example in this tutorial.
To implement LRT as ~\ref{equ:likelihood}, we need to get estimation for \hat{\theta}
<<theta estimate>>=
# estimate theta 
## theta<-cfa(model,data=Data,group="g",group.equal="loadings")
@
Then we can get estimate for group A and group B. 
<<theta A and theta B estimate>>=
# estimate theta A,B 
## thetaAB<-cfa(model,data=Data,group="g")
@
In the end, we can get the LRT results by calling the measurement invariance function in lavaan. 
<<LRT>>=
# LRT
## measurementInvariance(model,data=Data,group="g",strict=FALSE)
@
\subsection{Extensions for Unknown Group}

>>>>

where $x_{i}$ is the data vector for individual $i$, $t_{i}$ is the latent variable for variable $i$ that the scales purport to measure, and $f$ is the model's distributional form {addref}. If the cut point of $v$ is known in advance, i.e. gender, nested multiple group models {addref} coupled with likelihood ratio test are most commonly applied. 
Suppose there are two groups A and B. The null hypothesis of measurement invariance is

@@

To be more specific, in the following section, we will introduce how to implement multi group analysis in lavaan package. For more details, see {addref}
\subsection{Multiple Group Analysis}
First of all, we need to read in data to R.  
<<read data>>=
# Reading in the data
## (need data here)Data <- read.table("example.dat")
## names(Data) <- c("y1","y2","y3","y4","y5","y6","g")
@
Second, the model need to be specified using lavaan package. 
<<specify model>>=
library(lavaan)
model <- 'f1=~NA*y1+y2+y3
          f2=~NA*y4+y5+y6
          f1 ~~1*f1
          f2 ~~1*f2'
@
Third, we want to test which parameter(s) violate measurement invariance. In lavaan package, loading, manifest variables' intercept and factor means could be tested together or specifically. For more details, please see {addref}. Since in most cases researchers are interested in the factor loading invariance, we will use that as the example in this tutorial.
To implement LRT as ~\ref{equ:LRT}, we need to get estimation for $\hat{\theta}$, without differing groups.

<<theta estimate>>=
# estimate theta 
## theta<-cfa(model,data=Data,group="g",group.equal="loadings")
@
Then we can get estimate for group A and group B. 
<<theta A and theta B estimate>>=
# estimate theta A,B 
## thetaAB<-cfa(model,data=Data,group="g")
@
In the end, we can get the LRT results by calling the measurement invariance function in lavaan. 
<<LRT>>=
# LRT
## measurementInvariance(model,data=Data,group="g",strict=FALSE)
@
\subsection{Extensions for Unknown Group}
